---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# idswb

<!-- badges: start -->
<!-- badges: end -->
```{r}

```

`idswb` is primarily a data package enabling an efficient method for working with [International Debt Statistics from World Bank](https://www.worldbank.org/en/programs/debt-statistics/ids) in R.

## Installation

You can install the development version of idswb from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Teal-Insights/idswb")
```

This package will likely never be published on [CRAN](https://cran.r-project.org/) because the data file sizes are too big.


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(idswb)

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

